%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Sebastien Blanchet <s3blanch@edu.uwaterloo>
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%---------------------------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%---------------------------------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[mm]{res}

% Default font is the helvetica postscript font
%\usepackage{helvet}
\usepackage{xspace}
\usepackage{fontawesome}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=false,
}
\usepackage{geometry}
\geometry{
  letterpaper,
  left=0.5in,
  top=0.5in
}

% Increase text height
\textheight=720pt
\textwidth=446pt

% Spacing in between jobs and projects
\parskip=6pt

% Custom commands
\newcommand{\tb}{\textbullet \xspace}
\newcommand{\toprule}{
\vspace{6pt}
\nointerlineskip	% so I have this code
\moveleft\hoffset\vbox{\hrule width 540pt height 0.5pt}
\nointerlineskip
}

\newcommand{\npspctoprule}{
\nointerlineskip	% so I have this code
\moveleft\hoffset\vbox{\hrule width 540pt height 0.5pt}
\nointerlineskip
}

\begin{document}


%---------------------------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%---------------------------------------------------------------------------------------------------------
%% Simple name
%\name{SEBASTIEN BLANCHET}

%% Complex name
\name{SEBASTIEN BLANCHET
\href{https://github.com/sebastienblanchet}{\faGithub}
\href{https://www.linkedin.com/in/sebastien-blanchet/}{\faLinkedinSquare}
\href{https://sebastienblanchet.github.io}{\faGlobe}
}

\fontsize{9.5pt}{10pt}\selectfont

% Don't modify when hyper link is addedx
\urlstyle{same}

%\address{Waterloo, ON, CAN}
\address{\faMapO \xspace Cupertino, CA, USA}
\address{\faMobilePhone \xspace (669)-241-8438}
\address{\faPaperPlaneO \xspace s3blanch@edu.uwaterloo.ca}

%---------------------------------------------------------------------------------------------------------

\begin{resume}

%---------------------------------------------------------------------------------------------------------
%	SKILLS
%---------------------------------------------------------------------------------------------------------
\npspctoprule
%\faCogs \faSliders
\section{\faSliders \xspace SKILLS \xspace}
􏰚\tb Advanced embedded control system design acquired from project and hands-on laboratory experiences \\
􏰚\tb Exceptional critical thinking and problem-solving skills allowing for complex engineering analysis \\
􏰚\tb Highly motivated and organized self-starter with a strong attention to detail and work ethic \\
􏰚\tb Outstanding oral and written communication to share creative ideas fluently in both English and French \\
􏰚\tb Able to thrive and lead in a team or work independently in a dynamic deadline driven environment \\
%\tb Proficient in MS Office, SOLIDWORKS, MATLAB/Simulink, VBA/VB, Python, C++, C, LabVIEW, \LaTeX \xspace , Bash \\
\tb Proficient in iWork, SOLIDWORKS, MATLAB/Simulink, Python, C++, C, LabVIEW, \LaTeX \xspace , Bash \\
\tb Experience with PLC/SCADA/HMI systems, embedded microcontroller
programming (Texas Instruments, Arduino, x86 Assembler), Xilinx FPGA, Linux, ECAD tools, ANSYS FEA and CFD
%---------------------------------------------------------------------------------------------------------

\toprule
%---------------------------------------------------------------------------------------------------------
%	EDUCATION
%---------------------------------------------------------------------------------------------------------
\section{\faGraduationCap \xspace EDUCATION \xspace}
% Modify layout
\begin{format}
\employer{l}\location{r}\\
\title{l}\dates{r}\\
\end{format}

\employer{\textbf{\href{https://uwaterloo.ca}{University of Waterloo}}}
\location{\textbf{Waterloo, ON, CAN}}
\title{Candidate for B.ASc. \textsl{3.3/4.0 GPA}\\
Honours Mechanical Engineering Co-op Program}
\dates{\textsl{Sept. 2013 - Present}}
\begin{position}
\end{position}

%---------------------------------------------------------------------------------------------------------

\toprule
%---------------------------------------------------------------------------------------------------------
%	EXPERIENCE
%---------------------------------------------------------------------------------------------------------
% \faSuitcase \faBlackTie
\section{\faBlackTie \xspace EXPERIENCE \xspace}
% Modify layout
\begin{format}
\employer{l}\location{r}\\
\title{l}\dates{r}\\
\body\\
\end{format}

% Apple: Co-op 6
\employer{\textbf{\href{https://www.apple.com}{Apple Inc.}}}
\location{\textbf{Cupertino, CA, USA}}
\title{\textsl{Controls Engineering: Special Projects Group (SPG)}}
\dates{\textsl{Aug. 2017 - Present}}
\begin{position}
\tb Developed a HIL system to validate power electronic C control algorithms for autonomous technologies\\
\tb Emulated and optimized plant models on 32-bit Xilinx FPGA for high fidelity, low latency $\mu$s control \\
\tb Deployed LabVIEW HMI for deterministic communication between PC, PXIe RTOS controller and FPGA \\
\tb Flashed microcontroller via JTAG, serial and Ethernet with the latest software builds for bring-up of PCBAs \\
\tb Employed Agile software development with Atlassian tools and Git to track firmware bugs and fixes \\
\tb Applied DSP theory to convert continuous Simulink filters to discrete FIR firmware in C for data acquisition\\
\tb Debugged high voltage hardware with in-house test racks, electronic lab equipment, and NI instrumentation \\
\tb Assured robustness and reliability of safety-critical diagnostics by virtual fault injection at HIL\\
\tb Designed system harness to interface HIL and PCBA from electrical schematics and NI hardware datasheets
% \tb Converted continuous time MATLAB/Simulink algorithms to discrete firmware in C \\
% \tb Applied DSP theory with discrete filters in C for data acquisition (LPF, HPF, BSF, BPF, anti-alias) \\
% \tb Hardware communication protocols interfaces serial, ethernet, SPI PCIe, I2C, UART, JTAG \textbf{physical port interface of OSI software layering} \\
% \tb Acquire and generate analog and digital signals, control timing, and implement signal processing on RT and FPGA parallel processing\\
\end{position}

% Altaeros: Co-op 5
\employer{\textbf{\href{http://www.altaeros.com}{Altaeros Energies}}}
\location{\textbf{Boston, MA, USA}}
\title{\textsl{Systems Engineering}}
\dates{\textsl{Jan. - Apr. 2017}}
\begin{position}
\tb Performed FEA in ANSYS and Python on a prototype of an autonomous aerostat's electromechanical system \\
\tb Coordinated with vendors and ControlEng SERVOsoft to size all control system components (servos, VFDs) \\
\tb Utilized electronic lab equipment and LabVIEW HMI to log test data and analyze with MATLAB
\end{position}

% ODI: Co-op 4
\employer{\textbf{\href{https://www.ontariodie.com}{Ontario Die International Inc.}}}
%\employer{\textbf{{Ontario Die International Inc.} \xspace\href{https://www.ontariodie.com}{\faGlobe \faExternalLink}}}
\location{\textbf{Kitchener, ON, CAN}}
\title{\textsl{Research \& Development}}
\dates{\textsl{May - Aug. 2016}}
\begin{position}
\tb Designed robotic components (electrical, hydraulic) of PLC/CNC bending systems in SOLIDWORKS \\
%\tb Improved existing technology by applying lean, DFM and DFA principles to prototyping and research projects \\
\tb Automated tedious SOLIDWORKS tasks in VBA and C++ with the API in MS Visual Studio IDE \\
\tb Performed hands-on Q\&A HMI testing, machined components, fabricated assemblies with power/hand tools
\end{position}

% PWC: Co-op 3
\employer{\textbf{\href{http://www.pwc.ca}{Pratt \& Whitney Canada}}}
\location{\textbf{Mississauga, ON, CAN}}
\title{\textsl{Operations Program Management}}
\dates{\textsl{Sept. - Dec. 2015}}
\begin{position}
\tb Assured on time OEM delivery of a quality turbofan engine while meeting their expectations and needs \\
\tb Developed Excel VBA programs allowing for improvements in methods of business metric preparation
%\tb Collaborated with a multi-disciplinary team to develop logistics plans for new design incorporation
\end{position}

% Skyjack: Co-op 2
\employer{\textbf{\href{http://www.skyjack.com}{Skyjack Inc.}}}
\location{\textbf{Guelph, ON, CAN}}
\title{\textsl{Manufacturing Engineering}}
\dates{\textsl{Jan. - Apr. 2015}}
\begin{position}
\tb Worked with a team of engineers to troubleshoot production issues at an aerial work platform manufacturer
%\tb Increased process efficiency by organizing assembly stations and designing of jigs/fixtures with SOLIDWORKS
\end{position}

% % Nor Arc: Co-op 1
% \employer{\textbf{\href{http://www.norarc.com/en/}{Nor-Arc Steel Fabricators}}}
% \location{\textbf{Earlton, ON, CAN}}
% \title{\textsl{Junior Detailer}}
% \dates{\textsl{June - Aug. 2014}}
% \begin{position}
% \tb Detailed architectural, mechanical and electrical drawings including GD\&T in AutoCAD
% \end{position}

%---------------------------------------------------------------------------------------------------------

\toprule
%---------------------------------------------------------------------------------------------------------
%	PROJECTS
%---------------------------------------------------------------------------------------------------------
\section{\faPencilSquareO \xspace PROJECTS \xspace}
% Modify layout
\begin{format}
\title{l}\employer{l}\dates{r}\\
\body\\
\end{format}

% % Ball and Beam [CTL]
% \title{\textsl{Latest Proj}}
% \employer{\textsl{Personal}}
% \dates{\textsl{Ongoing}}
% \begin{position}
% \tb next
% \end{position}

% Ball and Beam [CTL]
\title{\textsl{Ball \& Beam Lab}}
\employer{\textsl{ECE481: Digital Control Systems}}
\dates{\textsl{Aug 2017}}
\begin{position}
\tb Designed LabVIEW HMI, performed system ID, implemented/tuned digital controller on NI cRIO FPGA
\end{position}

% % Python Design Altaeros [CAE]
% \title{\textsl{Python Design Optimization}}
% \employer{\textsl{WKRPT 400: Co-op 5}}
% \dates{\textsl{Apr. 2017}}
% \begin{position}
% \tb Developed Python script to solve material sizing algorithm, presented findings in \LaTeX report
% \end{position}

% Drumming Hack [CTL]
\title{\textsl{Drum Rhythm Arduino Hack}}
\employer{\textsl{Personal: WIT Hackathon}}
\dates{\textsl{Mar. 2017}}
\begin{position}
\tb Coded firmware in C and communicated over UART to MATLAB for real-time monitoring of vibration
\end{position}

% Wind turbine [CTL]
\title{\textsl{Wind Turbine Pitch Actuator}}
\employer{\textsl{ME360: Control Systems}}
\dates{\textsl{Dec. 2016}}
\begin{position}
\tb Studied time/frequency domain responses in MATLAB for closed-loop stability of PI controlled Simulink
\end{position}

% Mining device [CTL]
\title{\textsl{Mining Safety Device}}
\employer{\textsl{ME380: Engineering Design}}
\dates{\textsl{Nov. 2016}}
\begin{position}
\tb Developed a 3D printed enclosure to protect internal Arduino and sensors of severe underground environment
%\textsl{design and test}
\end{position}

% DC Motor [CTL]
\title{\textsl{DC Motor Control System}}
\employer{\textsl{ME360: Control Systems}}
\dates{\textsl{Oct. 2016}}
\begin{position}
\tb Designed PID control in Simulink for a DC motor; implemented in real-time with QUARC C code generation
\end{position}

% ODI CNC bending [CTL]
\title{\textsl{CNC Bending Powertrain}}
\employer{\textsl{WKRPT 300: Co-op 4}}
\dates{\textsl{Sept. 2016}}
\begin{position}
\tb Performed iterative testing with HMI to gather data for selection; assured compatibility into control system
\end{position}

% Dune Buggy [HO]
\title{\textsl{Dune-Buggy Magneto Repair}}
\employer{\textsl{Personal}}
\dates{\textsl{Aug. 2016}}
\begin{position}
\tb Diagnosed fuel system ignition issue then replaced coil and armature of solid-state system
\end{position}

% % SOLIDWORKS Drawing package [SW]
% \title{\textsl{SOLIDWORKS Add-In Development}}
% \employer{\textsl{WKRPT 300: Co-op 3}}
% \dates{\textsl{July. 2016}}
% \begin{position}
% \tb Accelerated assembly drawing package preparation by developing a VB add-in with the MS Visual Studio IDE
% \end{position}
%
% % PWC VBA [SW]
% \title{\textsl{VBA Software Development}}
% \employer{\textsl{WKRPT 200: Co-op 3}}
% \dates{\textsl{Dec. 2015}}
% \begin{position}
% \tb Programmed a report generating VBA project to extract and reduce SAP enterprise software data
% \end{position}

% Embedded Robot Design [SW]
\title{\textsl{Embedded Robot Design}}
\employer{\textsl{GENE 121: Digital Computation}}
\dates{\textsl{Apr. 2014}}
\begin{position}
\tb Coded a C++ algorithm, designed and assembled a robot to perform a colour sorting and movement operation
\end{position}

%---------------------------------------------------------------------------------------------------------

\toprule
%---------------------------------------------------------------------------------------------------------
%	INTERESTS
%---------------------------------------------------------------------------------------------------------
% \faGamepad \faLaptop \faDribbble \faMotorcycle
\section{\faMotorcycle \xspace INTERESTS \xspace}
􏰚\tb Further developing skills related to firmware, electronics and machine learning and artificial intelligence\\
􏰚\tb Repairing off-road vehicles, DIY electronics, hockey, golf, swimming and socializing with friends
%---------------------------------------------------------------------------------------------------------

\end{resume}
\end{document}

%% TODO
% spell check
